Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Comment on variable split - modification

\comment{Split the next sentence up into two paragraph: what is shown in each of the figures, what are the immediate conclusions? chuck out the gaming hours from figure \ref{fig:visualaptitudects}, that's a demograph, so move it to the other plot (I am aware that nine demographics are easier to display than ten, but content trumps). What happened to the arts skills? I seem to have a positive association now - why is my data different from yours?}
Results are presented graphically in figures \ref{fig:visualaptitudects} and \ref{fig:visualaptitudecat}.

>>>>

\comment{
Split the next sentence up into two paragraph: what is shown in each of the figures, what are the immediate conclusions? chuck out the gaming hours from figure \ref{fig:visualaptitudects}, that's a demograph, so move it to the other plot (I am aware that nine demographics are easier to display than ten, but content trumps). \\

Actually, they were split up like that because of continuous vs. categorical. It's not easy to facet when you have different $x$ scales. I've removed video games entirely for the time being. 
}
Results are presented graphically in figures \ref{fig:visualaptitudects} and \ref{fig:visualaptitudecat}.
